A reproducible journal article with RMarkdown&#58; A  building science template with examples for beginners based on the Elsevier journal format

### 2019-02-27 Paper/Manuscript.Rmd
Add grateful note + spellcheck info

@@

```{r echo=TRUE, message=FALSE, warning=FALSE}
# Example of generating BibTex file for the packages listed below
# Note the output location is specified 
pkgs <- c("here", "knitr", "ggpmisc", "gt", "grateful", "base", "rticles", "bookdown", 
          "rmarkdown")
cites <- grateful::get_citations(pkgs, filename = "pkg-refs.bib",
                    out.dir =  here("/Paper/SupplementaryMaterial/Software_citations") )
```

>>>>

## Spellcheck
If you are using RStudio, press F7 or go to `Edit` --> `Check spelling` in the menu.

@@

```{r echo=TRUE, message=FALSE, warning=FALSE}
# Example of generating BibTex file for the packages listed below
# Note the output location is specified 
# Note tidyverse is not included in the list below because it's a large package to install on Binder, if you are running this on your own computer I recommend including it if you want to cite it
pkgs <- c("here", "knitr", "ggpmisc", "gt", "grateful", "base", "rticles", "bookdown", 
          "rmarkdown")
cites <- grateful::get_citations(pkgs, filename = "pkg-refs.bib",
                    out.dir =  here("/Paper/SupplementaryMaterial/Software_citations") )
```
